Quantitative Auditing of AI Fairness with Differentially Private Synthetic Data

### 2025-01-21 paper/paper.tex
minor

This research is conducted in Python Jupyter notebooks and is publicly available.

@@

@@

The average of the differences between the fairness measure values of the original and synthetic datasets is below $0.1$ for all datasets across all models. Judging from different metrics, datasets, and models, this indicates that synthetic data is a good approximation of the original data in terms of fairness.

>>>>

@@

This research is conducted in Python Jupyter notebooks and is publicly available. The experiments were conducted on a macOS laptop with an Intel Core i9-9880H CPU (2.3GHz) and 32GB of RAM.

@@

The average of the differences between the fairness measure values of the original and synthetic datasets is below $0.1$ for all datasets across all models. Different models applied to the same datasets can yield different results, and judging from different metrics, datasets, and models, this indicates that synthetic data is a good approximation of the original data in terms of fairness.
